%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{Lufthansa Innovation Hub} % Organization
{Budapest, Hungary (Remote)} % Location
{Feb. 2022 - Present} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Developing applications for partners in the travel industry.}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{Ascenda Loyalty} % Organization
{Budapest, Hungary (Remote)} % Location
{Feb. 2019 - Feb. 2022} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Implementing tools, services and pipelines to provide data to a booking and loyalty platform.}
    \item {Main contributor of a Reporting application that consumes data across multiple services and publishes results to our partners.}
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {BSSN Software (Merck Group)} % Organization
    {Budapest, Hungary (Remote)} % Location
    {Nov. 2015 - Feb. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing algorithms, services and CRUD applications to process scientific data.}
		    \item {Interviewing/onboarding and supporting junior colleagues.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Lambda-Com (WebEye Group)} % Organization
    {Budapest, Hungary} % Location
    {Jun. 2014 - Nov. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As a member of a scrum team taking part in the development of several web applications for vehicle tracking.}
        \item {Developing tools for data verification.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
